---
title: "Music Insights"
author: "Reece Resendez"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

First, we need tidyverse to handle the data importing and wrangling
Since we already have it installed on this system we can go ahead and implement it.
```{r}
suppressMessages(library(tidyverse))
suppressMessages(library(readr))

suppressMessages(
survey <- read_csv(
  "https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv"))

suppressMessages(
preferences <- read_csv(
  "https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv"))


```
Now we want to go ahead and update all the column names for each of the dataframes to make referencing and appearance look better.
```{r}
colnames(survey)[colnames(survey) == 
    "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"

colnames(survey)[colnames(survey) == 
    "What is your pseudonym?"] <- "pseudonym"

colnames(survey)[colnames(survey) == 
    "Sex"] <- "sex"

colnames(survey)[colnames(survey) == 
    "Major"] <- "academic_major"

colnames(survey)[colnames(survey) == 
    "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"

colnames(survey)[colnames(survey) == 
    "Year you were born (YYYY)"] <- "year_born"

colnames(survey)[colnames(survey) == 
    "Academic Year"] <- "academic_level"

colnames(survey)[colnames(survey) == 
    "YOB"] <- "year_born"

colnames(survey)[colnames(survey) == 
    "Artist"] <- "favorite_song_artist"

colnames(survey)[colnames(survey) == 
    "Song"] <- "favorite_song"

colnames(survey)[colnames(survey) == 
    "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"

colnames(survey)[colnames(survey) == 
    "Timestamp"] <- "time_submitted"


colnames(survey)

```

We want to make the code tidy so we are going to use two packages that come with tidyverse but need to be loaded in to work.
```{r}
suppressMessages(library(dplyr))
suppressMessages(library(tidyr))

```

Now we are going to move into creating seperate tables from these two dataframes we have. We will do this by using dplyr and tibbles. We are also going to manipulate the data for a few variables to standardize them and create proper levels for categorical variables.
```{r}
Person <- tibble(time_submitted = survey$time_submitted, 
    pseudonym_generator = survey$pseudonym_generator, 
    pseudonym = survey$pseudonym, sex = survey$sex, 
    year_born = survey$year_born, academic_level = survey$academic_level, 
    academic_major = survey$academic_major, 
    favorite_instrument = survey$instrument_list)

Person$academic_level <- as.factor(Person$academic_level)
Person$academic_major <- as.factor(Person$academic_major)

# Standardize spelling of variables for
# major
levels(Person$academic_major)[levels(Person$academic_major) == 
    "Computer information systems"] <- "Computer Information Systems"

colnames(Person)

#------------------------------------------------------------------

FavoriteSong <- tibble(pseudonym = survey$pseudonym, 
    song_artist = survey$favorite_song_artist, 
    favorite_song = survey$favorite_song, 
    song_link = survey$favorite_song_link)

colnames(FavoriteSong)

#------------------------------------------------------------------
# This part was tricky. I manipulated the
# original dataframe preferences by using
# the gather function from Dplyr. This
# allowed me to lengthen data that was too
# wide by taking all the columns and
# making those rows under column name
# song_to_rate, then stored the ratings as
# keys called ratings.

preferences <- preferences %>% gather(song_to_rate, 
    rating, 3:45)

# using this new manipulated preferences
# dataframe I can easily map the columns
# to my ratings tibble

Ratings <- tibble(pseudonym = preferences$`What was your pseudonym?`, 
    song_to_rate = preferences$song_to_rate, 
    ratings = preferences$rating)

Ratings$song_to_rate <- as.factor(Ratings$song_to_rate)
```


Time to manipulate the timestamps column in Person. We will be using a couple functions to format this column properly.
```{r}

Person$time_submitted <- as.POSIXlt(parse_datetime(Person$time_submitted, 
    format = "%m/%d/%y %H:%M"))


```





```{r}


```


