---
title: "Music Insights"
author: "Reece Resendez"
output: html_notebook
---

First, we need tidyverse to handle the data importing and wrangling
Since we already have it installed on this system we can go ahead and implement it.
```{r}
suppressMessages(library(tidyverse))

suppressMessages(survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv"))

suppressMessages(preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv"))

```
Now we want to go ahead and update all the column names for each of the dataframes to make referencing and appearance look better.
```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"

colnames(survey)[colnames(survey) == "What is your pseudonym?"  ] <- "pseudonym"

colnames(survey)[colnames(survey) == "Sex"] <- "sex"

colnames(survey)[colnames(survey) == "Major"] <- "academic_major"

colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)" ] <- "instrument_list"

colnames(survey)[colnames(survey) == "Year you were born (YYYY)"  ] <- "year_born"

colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"

colnames(survey)[colnames(survey) == "YOB"] <- "year_born"

colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"

colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"

colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"

colnames(survey)[colnames(survey) == "Timestamp"] <- "time_submitted"


colnames(survey)

```

We want to make the code tidy so we are going to use two packages that come with tidyverse but need to be loaded in to work.
```{r}
suppressMessages(library(dplyr))
suppressMessages(library(tidyr))

```

Now we are going to move into creating seperate tables from these two dataframes we have. We will do this by using dplyr and tibbles
```{r}
Person <- tibble(time_submitted = survey$time_submitted,
   pseudonym_generator = survey$pseudonym_generator,
   pseudonym = survey$pseudonym,
   sex = survey$sex,
   year_born = survey$year_born, 
   academic_level = survey$academic_level,
   academic_major = survey$academic_major)

colnames(Person)

#------------------------------------------------------------------

FavoriteSong <- tibble(pseudonym = survey$pseudonym,
      song_artist = survey$favorite_song_artist,
      favorite_song = survey$favorite_song,
      song_link = survey$favorite_song_link)

colnames(FavoriteSong)

```



